Figures

### 2020-02-26 figures/02_depth_model.Rmd
add residual density plots facetting by class

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = shape_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = reservoir_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)
```

>>>>

gg_shape <- ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  facet_wrap(~ model) + 
    theme(legend.position = "bottom",
        strip.background = element_blank(), 
        strip.text = element_blank(),
        plot.margin = unit(c(1.2,0.2,0.2,0.2), "cm"))  +
  guides(fill = guide_legend(nrow = 2))

gg_shape <- ggdraw(gg_shape)  +
  # draw_label("proxy", x = 0.83, y = 0.32, angle = 270, size = 10) +
  # draw_label("true", x = 0.83, y = 0.65, angle = 270, size = 10) +
  # draw_label("slope", x = 0.93, y = 0.5, size = 10, angle = 270) +
  draw_label("proxy", x = 0.7, y = 0.89, size = 10) +
  draw_label("true", x = 0.3, y = 0.89, size = 10) +
  draw_label("distance", x = 0.5, y = 0.94, size = 10)# +
  #draw_label("Shape class", x = 0.5, y = 0.98, size = 10, fontface = "bold")

gg_reservoir <- ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = reservoir_class), alpha = 0.75, adjust = 1.3) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  facet_wrap(~ model) +
  theme(legend.position = "bottom",
        strip.background = element_blank(), 
        strip.text = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = unit(c(1.2,1.2,0.2,0.2), "cm")) +
  guides(fill = guide_legend(nrow = 2))

gg_reservoir <- ggdraw(gg_reservoir) +
  draw_label("proxy", x = 0.83, y = 0.44, angle = 270, size = 10) +
  draw_label("true", x = 0.83, y = 0.77, angle = 270, size = 10) +
  draw_label("slope", x = 0.93, y = 0.62, size = 10, angle = 270) +
  draw_label("proxy", x = 0.7, y = 0.89, size = 10) +
  draw_label("true", x = 0.3, y = 0.89, size = 10) +
  draw_label("distance", x = 0.5, y = 0.94, size = 10)# +
  # draw_label("Reservoir class", x = 0.5, y = 0.98, size = 10, fontface = "bold")

cowplot::plot_grid(gg_shape, gg_reservoir, 
                   nrow = 1, rel_widths = c(1, 0.95))
```

### 2020-02-26 manuscript/figures.Rmd
add residual density plots facetting by class

### 2 x 4 grid of residual box plots for shape and reservoir by true and proxy dist/slope (6)

>>>>

```{r depth_model_grid_resid, fig.cap = "Depth model residuals by shape and reservoir class.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_grid_resid-1.pdf")
```
